### 2018-05-18 Writing/disparity_review.tex
Edits to adpt

\section{Future directions}
As mentioned above, there is no ``one-size-fit-all'' morphological disparity analysis pipeline.
As in any multidimensional analysis, there are a lot of nuances in which data to use and how to analyse it, all stemming from the explicit formulation of the disparity hypothesis.
To understand these nuances, it is important to remember that: (1) morphological disparity analysis are not new and much effort has been made in developing the our methods and (2) multidimensional analysis are by far not restricted to morphological data analysis and solutions to specific problems can be found in the literature that is not necessary focused on morphology (especially ecology and mathematics).

We believe that many of the caveats in morphological disparity analysis can arise when ``blindly'' applying methodological pipelines that can come at the expense of loosing sight of the actual biological question tested.
We therefore advice to keep the methodology simple and tractable, at least in the preliminary analysis.
Also, many of the caveats and technical problems in disparity analysis have been tackled in other fields namely ecology.
In fact, ecological questions are often closely related to evolutionary ones and ecological data is also often multidimensional [CITE DONOHUE's papers].

>>>>

\section{Future directions}
As mentioned above, there is no ``one-size-fits-all'' morphological disparity analysis pipeline.
As with any multidimensional analysis, there are many nuances in deciding which data to use and how to analyse it, stemming from the explicit formulation of the disparity hypothesis.
To understand these nuances, it is important to remember that: (1) morphological disparity analyses are not new and much effort has been made in developing methods; and (2) multidimensional analyses are not restricted to morphological data analysis and solutions to specific problems can be found in literature that is not necessary focused on morphology (especially ecology and mathematics).

We believe that many of the caveats in morphological disparity analysis can arise when ``blindly'' applying methodological pipelines at the expense of losing sight of the  biological question being tested.
We therefore advise keeping the methodology simple and tractable, at least in the preliminary analysis.
Also, many of the caveats and technical problems in disparity analyses have been tackled in other fields, mainly ecology.
This is perhaps unsurprisingly as ecological questions are often closely related to evolutionary questions, and ecological data is also often multidimensional [CITE DONOHUE's papers].
